Catchability_ecov_sims

### 2023-09-29 Ecov_study/catchability/Catchability_ecov_sims.Rmd
Fix error in OM loop so actually walks through subsetOM object, note on EM model_name.

Load packages & source functions used in simulation testing
```{r}
## Packages
library(tidyverse)
library(wham)
library(TAF)

@@

### Set up OM and corresponding EMs based on above factorial variations (need only be run once)
- No stock-recruit relationship is implemented (as in project 0) so a variation of make_om() is used here to:
  - 1) Set Fmsy equal to the F40% proxy
  - 2) Estimate equilibirum initial numbers at age by setting NAA_re$N1_model = 1 rather than using the S-R
- By default, the environment only impacts catchability for the fall (2nd) index. EM misspecifications are based off of this assumption.
- Each OM is stored in a separate directory with input objects for EMs that are misspecified based on this OM in a subdirectory of the OM
```{r}
n_fleets <- 1
n_indices <- 2
n_ages <- 10
n_years <- 40

@@

      # Set up EM name based on EMsetup
      input$model_name <- paste0("EM_", paste(unfactor(EMsetup[iem, ]), collapse = "_")) # Set up OM name based on OMsetup

@@

      # Set up EM name based on EMsetup
      input$model_name <- paste0("EM_", paste(unfactor(EMsetup[iem, ]), collapse = "_")) # Set up OM name based on OMsetup 
    }

@@

#### Amanda run Fhist = H-L simulations
```{r}
# Set number of simulations to run
nsim <- 2

# Subset of OMs to run
subsetOM <- OMsetup %>% filter(F_hist == "H-L")

@@

@@

# Subset of OMs to run
subsetOM <- OMsetup %>% filter(F_hist == "H-L") %>% filter(Ecov_effect != 0)
# EMs 
subsetEM <- EMsetup %>% filter(miss_season == "NONE") %>% filter(miss_q == "qRand" | miss_q == "NoEcov")

@@

# Subset of OMs to run
subsetOM <- OMsetup %>% filter(F_hist == "Fmsy") %>% filter(Ecov_effect != 0)
# EMs 
subsetEM <- EMsetup %>% filter(miss_season == "NONE") %>% filter(miss_q == "qRand" | miss_q == "NoEcov")

@@

@@

postprocess_simTestWHAM(filenames = files) 
```

@@

>>>>

Load packages & source functions used in simulation testing
```{r}
## Packages
library(tidyverse)
library(wham)
library(TAF)
library(varhandle)

@@

### Set up OM and corresponding EMs based on above factorial variations (need only be run once)
- No stock-recruit relationship is implemented (as in project 0) so a variation of make_om() is used here to:
  - 1) Set Fmsy equal to the F40% proxy
  - 2) Estimate equilibirum initial numbers at age by setting NAA_re$N1_model = 1 rather than using the S-R
- By default, the environment only impacts catchability for the fall (2nd) index. EM misspecifications are based off of this assumption.
- Each OM is stored in a separate directory with input objects for EMs that are misspecified based on this OM in a subdirectory of the OM
!!! EM model_name labels may be misslabeled, but file path labels for EM storage are correct so those are used in postprocessing
```{r}
n_fleets <- 1
n_indices <- 2
n_ages <- 10
n_years <- 40

@@

      # Set up EM name based on EMsetup
      input$model_name <- paste0("EM_", paste(unfactor(EMsetup[iem, ]), collapse = "_"))

@@

      # Set up EM name based on EMsetup
      input$model_name <- paste0("EM_", paste(unfactor(EMsetup[iem, ]), collapse = "_")) 
    }

@@

#### Amanda run Fhist = H-L simulations
```{r}
# Set number of simulations to run
nsim <- 2 # 2

# Subset of OMs to run
subsetOM <- OMsetup %>% filter(F_hist == "H-L") %>% filter(Ecov_effect != 0) %>%
  filter(OMname >100)
# %>% head(n=10)
subsetOM <- subsetOM[8:nrow(subsetOM),] #7?

@@

# Run simulation tests
for(iom in 1:nrow(subsetOM)){
  omdir <- here::here("Ecov_study", "catchability", "Results", paste0("OM_", subsetOM[iom, "OMname"]))

  # Pull OM
  testOM <- readRDS(here::here(omdir, paste0("OM_", subsetOM[iom, "OMname"], ".Rds")))

@@

# Subset of OMs to run
subsetOM <- OMsetup %>% filter(F_hist == "H-L") %>% filter(Ecov_effect == 0)
# EMs 
subsetEM <- EMsetup %>% filter(miss_season == "NONE") %>% filter(miss_q == "qRand" | miss_q == "NoEcov")

# Run simulation tests
for(iom in 1:nrow(subsetOM)){
  omdir <- here::here("Ecov_study", "catchability", "Results", paste0("OM_", subsetOM[iom, "OMname"]))

  # Pull OM
  testOM <- readRDS(here::here(omdir, paste0("OM_", subsetOM[iom, "OMname"], ".Rds")))

@@

# Subset of OMs to run
subsetOM <- OMsetup %>% filter(F_hist == "Fmsy") %>% filter(Ecov_effect == 0)
# EMs 
subsetEM <- EMsetup %>% filter(miss_season == "NONE") %>% filter(miss_q == "qRand" | miss_q == "NoEcov")

@@

  # Pull OM
  testOM <- readRDS(here::here(omdir, paste0("OM_", subsetOM[iom, "OMname"], ".Rds")))

@@

perfMet <- postprocess_simTestWHAM(filenames = files)

@@

### Plot results
```{r}
plotResults(results = perfMet, convergedONLY = TRUE)
```
